Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-06-07 reports/paper1/paper.tex
Revise paper

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams
}

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries. One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.

@@

Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT). The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.

XCT is commonly used for the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

The strength of XCT comes from the fact that the location of the pores can be visualised. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \linebreak\citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

It was investigated whenever defects can be detected from a single x-ray projection. This was done by obtaining an x-ray projection of a 3D printed sample, with purposely designed voids, and comparing it with the simulation. The apparatus and procedures are shown in the methods section. In addition, software development and simulation studies were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD of a 3D cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

@@

The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{px}\times \SI{256}{px}$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $\SI{30}{px}\times \SI{30}{px}$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{px}\times \SI{256}{px}$ contaminated Gaussian image with a $\SI{30}{px} \times \SI{30}{px}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>\SI{54}{px}$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{px} \times \SI{256}{px}$ filtered contaminated Gaussian image with a $\SI{30}{px}\times \SI{30}{px}$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeated measurements of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

@@

In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{px}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure*}

@@

For good results, the faces of the 3D printed cuboid were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to 3D printed samples with complicated geometry and curved surfaces.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise the 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

@@

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

>>>>

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Mark Williams \and Thomas Nichols \and Julia Brettschneider 
}

\DeclareSIUnit\pixel{px}
\DeclareSIUnit\adu{ADU}

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries \citep{wong2012review, ngo2018additive}. One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.

@@

Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT) \citep{kruth2011computed, sun2012overview}. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam. The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.

In AM, XCT is commonly used for the investigation of pores \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

The strength of XCT comes from the fact that the location of the pores can be visualised. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

It was investigated whenever defects can be detected from a single x-ray projection. This was done by obtaining an x-ray projection of an AM sample, with purposely designed voids, and comparing it with the simulation. The apparatus and procedures are shown in the methods section. In addition, software development and simulation studies were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD of a cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

@@

The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>\SI{54}{\pixel}$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeated measurements of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

@@

In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure*}

@@

For good results, the faces of the AM cuboid were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise the 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

@@

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The EM algorithm \citep{dempster1977maximum, bishop2006pattern} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
